### 2017-10-12 thesis/misc/appendix2.tex
Final revision completed

	The original result from the \citet{Gatza2010a} study were used to determine the directions of the GT pathway-associated genetic signatures in \cref{sec:pathway_associated_genetic_signatures_from_gatza2010a_study} (\cref{fig:gatza_paper_res}).

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/gtobrma}\\
		\caption[Heatmaps of all the obesity and the pathway metagenes in the CR, \gls{nzbc} and FM data]{Heatmaps showing the obesity metagenes from the CR data set with the gene expressions of the obesity-associated genetic signatures in the \gls{rma} normalised GT data set.
		High and low correlation were represented as red and blue, respectively, where the colours were matched with the values on the scale shown in the top left histogram.}
		\label{fig:appendix/ob_meta_dir_gt}
	\end{figure}

@@

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.8\linewidth,page=1]{results2/overlap}
		\caption[Heatmap showing the overlap of genes between the different pathway-associated signatures]{Heatmap showing the overlap of genes between the different pathway-associated signatures. For each pairs of pathway-associated signatures, the overlap of genes were counted and divided by the total number of unique genes from the two signatures to get a ratio. This ratio was then scaled and plotted as shown}
		\label{fig:overlap_pathway_genetic_signature_extra}
	\end{figure}

>>>>

	The original result from the \citet{Gatza2010a} study was used to determine the directions of the GT pathway-associated genetic signatures in \cref{sec:pathway_associated_genetic_signatures_from_gatza2010a_study} (\cref{fig:gatza_paper_res}).

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/gtobrma}\\
		\caption[Heatmaps of all the obesity and pathway metagenes in the CR, \gls{nzbc} and FM data]{Heatmaps showing the obesity metagenes from the CR data set with the gene expression of the obesity-associated genetic signatures in the \gls{rma} normalised GT data set.
		High and low correlation were represented as red and blue, respectively, where the colours were matched with the values on the scale shown in the top left histogram.}
		\label{fig:appendix/ob_meta_dir_gt}
	\end{figure}

@@

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.8\linewidth,page=1]{results2/overlap}
		\caption[Heatmap showing the overlap of genes between the different pathway-associated signatures]{Heatmap showing the overlap of genes between the different pathway-associated signatures. For each pair of pathway-associated signatures, the overlap of genes was counted and divided by the total number of unique genes from the two signatures to get a ratio. This ratio was then scaled and plotted as shown}
		\label{fig:overlap_pathway_genetic_signature_extra}
	\end{figure}
